Lost in space: the eco-evolutionary impacts of straying on metapopulation robustness

### 2017-06-02 Manuscript/CoverLetter/YGWM_cover.tex
final tweaks on figs

Our theory is analytic, relatively simple, and synthesizes a variety of fundamental ecological theories (energy equivalence hypothesis, resource competition theory, Cope’s rule, the fasting endurance hypothesis) and shows how many of these are the natural consequence of a simple dynamical framework that incorporates the energetic consequences of starvation and recovery combined with allometric timescales. 
We believe that our findings will be of general interest to ecologists, evolutionary biologists, and paleoecologists, such that consideration for publication in a broad interest journal such as \emph{Philosophical Transactions} is warranted.

>>>>

Our theory is general, relatively simple, and synthesizes a variety of fundamental ecological and evolutionary theories to show that our results are the natural consequence of a simple dynamical framework that incorporates the dispersal and local selection. 
We believe that our findings will be of general interest to ecologists, freshwater biologists, and evolutionary biologists, such that consideration for publication in a broad interest journal such as \emph{Philosophical Transactions} is warranted.
